\LaTeXe\ guide for the Journal of Functional Programming

### 2019-05-02 papers/jfp/2-background.tex
Fix typo

\begin{minted}[xleftmargin=10pt]{haskell}
"release.tar" %> \_ -> do
    need ["release.txt"]
    files <- lines <$> readFile "release.txt"
    need files
    system "tar" $ ["-cf", "release.tar"] ++ files
\end{minted}

>>>>

\begin{minted}[xleftmargin=10pt]{haskell}
"release.tar" %> \_ -> do
    need ["release.txt"]
    files <- lines <$> readFile "release.txt"
    need files
    cmd "tar" $ ["-cf", "release.tar"] ++ files
\end{minted}
